|

### 2021-03-17 appendix/appendix.Rmd
changes random effects

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(estims, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod,
                    filter(mod2, byvar==i) %>%
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

@@

In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models. The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect. The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sample and tests characteristics.

In this paper, we use a multi-level random effects model. The difference between a simple random effects model, and a multi-level random effects model is that we can specify multiple levels of empirical dependency in the data (). The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).

@@

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

mod <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

mod <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
f8 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
```

@@

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

build_forest_het(mod, capt = NULL, hetvar = aux$method)
```

@@

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
f9 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
```

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

build_forest_het(mod, capt = NULL, hetvar = aux$method)
```

For the RDD subgroup analysis, we can see a much clearer picture. All estimates are negative, and the subgroup effect is -0.11. This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") +
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") +
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))
f8b
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: \$I\^2 = \$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is \$g = \$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

mod <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")
mod
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

>>>>

# Build forest plot for heterogeneous analysis
build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {

  mod2 <- estim_het(dat = dat, 
                    yi = coef, 
                    v = v, 
                    random = ~ 1 | id_level1/id_level2, 
                    slab = slab, 
                    hetvar = hetvar)

  mod2 <- data.frame(mod2)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

@@

In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models. The fixed effects model assumes that there exists only one true effect, and that all estimates are an attempt to uncover this effect. The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.

In this paper, we a random-effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

Another crucial assumption in the meta-analysis is the independence between the results (@harrer2019doing, @cheung2019guide, @veroniki2016methods, @borenstein2011introduction). This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation. However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable. While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients. This because the papers report an average of `r mean(as.numeric(table(fulldat$id)))` coefficients. Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated. To correct for this problem, we use a multi-level random effects model (@cheung2014modeling). The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels. All these levels are assumed to absorb the dependence in the data, leaving for the main coefficient, the independent effect of legislature size on public spending.

There are two levels in the main models. First, we build a common index for papers that share the same dataset specifications. The papers with common indexing are:

| Paper IDs                                   | Source of Dependence                                                     |
|---------------------------------------------|--------------------------------------------------------------------------|
| 3, 42, 132, <br>165, 439, 441, <br>467, 505 | US States Dataset                                                        |
| 408, 208, A258                              | US Municipalities Dataset                                                |
| 849, 578                                    | US Municipalities Dataset<br>and Same Author in two<br>Different Studies |

All the remaining papers receive a unique index. As the number of the papers with these dependencies are not very high, and many characteristics within papers vary (e. g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs. In the case of the full dataset, the results change considerably, because authors fit several models within the same paper. In the case In any case, we use multi-level random effects for all the estimated models in this paper.

To study the possibility of of publication bias, for all models we add a funnel plot and an @egger1997bias test for distribution asymmetry. The funnel plot displays the possibility of having a file-drawer effect, meaning that null results are disproportionately less represented in our sample. In this plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome. If they are asymmetric, it evidences a possible file-drawer effect.

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [@harrer2019doing](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

f8 <- build_forest_het(aux, aux$coef, 
                       aux$VAR, slab = aux$authoryear,
                       capt = NULL, lsize = 15, 
                       ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
                       hetvar = aux$method)
```

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$method)
```

@@

```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

f9 <- build_forest(mod, capt = NULL, 
                       lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by RDD)')
```

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC', 
         method == 'RDD')

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")

build_forest(mod, capt = NULL, ttl = NULL)
```

For the RDD subgroup analysis, we can see a much clearer picture. The subgroup effect is -0.085. This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

mod <- rma.mv(coef, VAR, data=aux,
          slab=paste(authoryear),
          test = 't',
          random = ~ 1 | id_level1/id_level2, 
          tdist = TRUE,
          method = "REML")
mod
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```
